Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-24 text/src/article.tex
Update references for first results section

The scaffold file specifies how contigs should be joined together in the draft
genome sequence. The raw nucleotide sequence for each contig is stored in
a fasta file, as might be produced from assembly of sequencing reads using
programs such as newbler\cite{newbler} or abyss\cite{abyss}. Scaffolder then
the contig to be selected by specifying the name of the contig in the scaffold
file. The scaffold file also allows a sub-sequence or the reverse complement of
a contig to used. This therefore preserves the original sequence data but also
allowing sequences to manipulated in the final genome build.

>>>>

The scaffold file specifies how contigs should be joined together in the draft
genome sequence. The raw nucleotide sequence for each contig is stored in
a fasta file, as might be produced from assembly of sequencing reads using
programs such as Newbler\cite{miller2010} or ABySS\cite{simpson2009}.
Scaffolder then the contig to be selected by specifying the name of the contig
in the scaffold file. The scaffold file also allows a sub-sequence or the
reverse complement of a contig to used. This therefore preserves the original
sequence data but also allowing sequences to manipulated in the final genome
build.
